GRN inference in multiple species

### 2015-04-30 paper1.tex
hi
more figures

@@

>>>>

\subsection{Beta scaling}
[INSERT JUSTIFICATION]
\\
In previous work, betas were rescaled as to form a matrix of confidence scores $S$ as follows
\begin{equation}
S_{i,j} = \frac{\sigma^2_{\text{full model for }y_j}}{\sigma^2_{\text{full model for }y_j \text{ without predictor }i}}
\end{equation}
Computing residuals with respect to the data alone would disregard information gained through fusion. Instead, we used an approximation
\begin{equation}
S_{i,j} = \frac{\sigma^2_{\text{full model for }y_j}}{\sigma^2_{\text{full model for }y_j} + B_{i,j}^2 \times var(TF_j)}
\end{equation}
When the residual is uncorrelated with the prediction, then removing regressor $i$ with weight $B_{i,j}^2$ from the model of $j$ will increase the residual by $B_{i,j}^2$ times the variance of regressor $i$. In the case of regularized regression, the regressor and residual need not be uncorrelated, so the approximation will not hold exactly. This scaling is similar to rescaling according to variance explained relative to an augmented design matrix that includes fusion constraints. We use an approximation because it is simpler to compute. The intuition is that a large $B_{i,j}$ may be necessary because TF $i$ varies little across the available data, and these large weights are not suggestive of a true regulatory interaction.

@@

\begin{figure}
\begin{center}
  \includegraphics[scale=0.45]{waka7unnormed.png}
  \caption{\label{fig:figure1} precision recall curves of constrained interactions for several values of lamS, computed across folds containing $\frac{1}{15}th$ of the available B. Subtilis data}
  \end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[scale=0.45]{woko7.png}
  \caption{\label{fig:figure1} normalized precision recall curves of constrained interactions for several values of lamS, computed across folds containing $\frac{1}{15}th$ of the available B. Subtilis data. Normalization involved dividing the precision each each recall level, for each curve, and for each cross-validation fold by the corresponding $\lambda_S=0$ precision.}
  \end{center}
\end{figure}

\begin{figure}
\begin{center}
  \includegraphics[scale=0.45]{wat7.png}
  \caption{\label{fig:figure1} As previous figure, but for all interactions.}
  \end{center}
\end{figure}
